\documentclass[11pt,letterpaper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{burgundy}
\setlength{\hintscolumnwidth}{2.5cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.8]{geometry}
\usepackage[maxbibnames=99,
			defernumbers=true,
			isbn=false,
			doi=false,
			url=false,
			sorting=ymdnt,
			backend=biber,
			style=numeric,
			giveninits=true]{biblatex}
\usepackage[sfdefault]{roboto}

\renewcommand*{\intitlepunct}{\space}
\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{
  	\begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
    \hfill
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
}
\newcommand{\cvreference}[8]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{~\texttt{#7}\newline}%
    \ifthenelse{\equal{#8}{}}{}{\phonesymbol~#8}}

\DeclareSortingScheme{ymdnt}{
  \sort{
    \field{presort}
  }
  \sort[final]{
    \field{sortkey}
  }
  \sort[direction=descending]{
    \field[strside=left,strwidth=4]{sortyear}
    \field[strside=left,strwidth=4]{year}
    \literal{9999}
  }
  \sort[direction=descending]{
    \field{month}
    \literal{9999}
  }
  \sort{
    \field{sortname}
    \field{author}
    \field{editor}
    \field{translator}
    \field{sorttitle}
    \field{title}
  }
  \sort{
    \field{sorttitle}
    \field{title}
  }
}

\AtDataInput{%
  \csnumgdef{entrycount:\therefsection:\thefield{entrytype}}{%
    \csuse{entrycount:\therefsection:\thefield{entrytype}}+1}}
    
\DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
\newrobustcmd*{\mkbibdesc}[1]{%
  \number\numexpr\csuse{entrycount:\therefsection:\thefield{entrytype}}+1-#1\relax}

\defbibenvironment{bibliography}
  {\list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}  

\name{Miguel}{Velez}
\title{Ph.D. Student in Software Engineering}
\address{Carnegie Mellon University}{School of Computer Science}{Institute for Software Research}
\email{mvelezce [at] cs.cmu.edu}
\homepage{http://www.cs.cmu.edu/\textasciitilde mvelezce/}
\social[linkedin]{miguelvelezmj25}

\quote{"Premature optimization is the root of all evil" -Donald Knuth}
  
\addbibresource{bibliography/bibliography.bib}  

\begin{document}

\makecvtitle

\section{Education}
\cventry{2016 - Present}{Ph.D. Software Engineering}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{Advisor: Christian K{\"a}stner.}
\cventry{2010 - 2015}{B.A. Computer Science (Physics minor) }{University of St Thomas}{St. Paul, MN}{USA}
	{Summa Cum Laude. Major and Minor GPA: 4.00/4.00. Cumulative GPA: 3.99/4.00.\\Advisor: Patrick Jarvis. Summa Cum Laude paper: ``Current and Future Relationships Between Robots and Humans''.}

\section{Research Experience}
\cventry{2016 - Present}{Graduate Research Assistant}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{}{}
\cventry{Summer 2015}{Research Intern}{Massachusetts Institute of Technology}{Cambridge, MA}{USA}{}
	{}
\cventry{2014 - 2015}{Undergraduate Student Researcher}{University of St. Thomas}{St. Paul, MN}{USA}{}
	{}
	
\section{Industry Experience}
\subsection{Full-time}
\cventry{2016}{Application Developer/Software Engineer}{Sportradar US}{Minneapolis, MN}{USA}
	{Accepted full-time offer. Developed an ETL application using Ruby that provided data for the NFL Radar360 research tool.}

\subsection{Internships}
\cventry{Summer 2018}{Software Engineering Intern}{Google}{Mountain View, CA}{USA}
	{Improved ranking of contact actions in AGSA Suggest.}
\cventry{Fall 2015}{Application Developer/Software Engineer}{Sportradar US}{Minneapolis, MN}{USA}
	{Built a Ruby monitoring application to parse and build Formula 1 feeds.}
\cventry{Spring 2015}{Jr. Application Developer}{SportsData/Sportradar US}{Minneapolis, MN}{USA}
	{Implemented an application to parse and build MLB feeds using Ruby.}
\cventry{2013 - 2015}{Cloud Developer Intern}{Valtira}{Minneapolis, MN}{USA}
	{Developed web applications with Java servlets, AngularJS, and MySQL databases.}

\section{Publications}
%\newrefcontext[labelprefix=C]
%VSJSAK:ICSE19,
\nocite{JVSK:FSE18,JSVKPA:ASE17,JVKSK:SEAMS17,VSIC:FiC16}
\printbibliography[heading=subbibliography,title={Refereed Conference Publications},type=inproceedings,resetnumbers=true]
%\newrefcontext[labelprefix=M]
\nocite{VJKSSA-BRASS17,VS:IUST16,VS:CCSC15,VS:MSRP15,V:SUMMA15,VGS:IUST14}
\printbibliography[heading=subbibliography,title={Miscellaneous},
type=misc,resetnumbers=true]

\section{Awards and Honors}
\cvitem{2015}{\textbf{MSRP Research Internship at MIT}. Acceptance rate: 10.5\%}
\cvitem{2015}{\textbf{CCSC:MW 1\textsuperscript{st} place Student Posters \& Showcase Discovery Track}. \$100}
\cvitem{2015}{\textbf{UST Student Travel Grant}. \$750}
\cvitem{2014, 2015}{\textbf{UST Collaborative Inquiry Grant}. \$2,000}
\cvitem{2012}{\textbf{UST International Student Leadership Scholarship}. \$500}
\cvitem{2011 - 2015}{\textbf{Bev and Pat Flaherty Scholarship}. \$14,000}
%\cvitem{\textbf{UST Dean's Honor List}, 2010-2015}
\cvitem{2010 - 2015}{\textbf{University of St. Thomas International Scholarship}. \$80,000}
\cvitem{2010 - 2015}{\textbf{University of St. Thomas Tuition Scholarship}. 40\% discount}
\cvitem{2008 - 2009}{\textbf{American Field Service International Scholarship}.}

%\section{Software and Products}
%\cvline{sqlplus}{A DSL to add alerts to various SQL DML events.\newline \textit{http://www.mijecu25.com/software/sqlplus/}}
%\cvline{cstats}{Generate information about your file directory.\newline \textit{http://www.mijecu25.com/software/cstats/}}
%\cvline{dsa}{Java library of data structures and algorithms.\newline \textit{http://www.mijecu25.com/software/dsa/}}
%\cvline{Cubie Cruiser}{2D endless runner game written in Unity focused on avoiding obstacles.\newline \textit{http://www.mijecu25.com/software/games/cubiecruiser.html}}
%\cvline{Urban Tennis}{First full game written in Unity published for the web.\newline \textit{http://www.mijecu25.com/software/games/urbantennis.html}}
%\cvline{Unity Game Development Manual}{Guide of the basics of Unity game development.\newline \textit{https://github.com/mijecu25/unity-manual}}
	
%\section{Selected Press}
%\cvlistitem{``CS Major's Research Poster Receives First Place at Conference.'' UST CISC Department, \textit{CISC Department News}, Oct. 2, 2015.}
%\cvlistitem{``Two CISC Majors Win Prestigious Research Opportunities.'' UST CISC Department, \textit{CISC Department News}, Apr. 2, 2015.}

\section{Service}
%\cventry{}{}{}{}{}{}
%\subsection{Reviewer}
%\subsection{Sub-Reviewer}
\cvitem{2017}{ASE'17 Sub-Reviewer}
\cvitem{2017}{FSE'17 Sub-Reviewer}
\cvitem{2017}{CMU REU-SE Committee member}
\cvitem{2016}{ICSE'17 Sub-Reviewer}

\section{Other Interests and Activities}
\cvitem{2018}{Hispanic Googler Network}
\cvitem{2014 - 2015}{UST Game Design Club}
\cvitem{2013, 2015}{Note taker. Helped two students with disabilities to take notes in class}
\cvitem{2012 - 2015}{UST Computer Science Consultant}
\cvitem{2011 - 2015}{UST Computer Science Club}
\cvitem{2010 - 2015}{UST Globally Minded Student Association}
\cvitem{2012 - 2013}{St. Thomas Activities and Recreation President}
\cvitem{2011 - 2012}{St. Thomas Activities and Recreation Intern}
\cvitem{2010 - 2012}{UST Spanish Tutor}
\cvitem{2011}{2 STEM Learning Communities}
\cvitem{2010 - 2011}{UST Morrison Hall Council}

\section{References}

\cvdoublecolumn{
	\cvreference{Christian K{\"a}stner}
    {Institute for Software Research}
    {Carnegie Mellon University}
    {}{}
    {kaestner [at] cs.cmu.edu}
    {}
    {+1 412 268 5254}
}
{
    \cvreference{James Worcester}
   	{Android Google Search App}
   	{Google}
   	{}{}
   	{jworcest [at] google.com}
   	{}
   	{+1 703 402 2084}	
}

\bigskip

\cvdoublecolumn{
	\cvreference{Pooyan Jamshidi}
   	{Computer Science and Engineering}
   	{University of South Carolina}
   	{}{}
   	{pjamshid [at] cse.sc.edu}
   	{}
   	{+1 412 519 8405}	
}
{
	\cvreference{Norbert Siegmund}
   	{Department of Computer Science}
   	{Bauhaus-Universität Weimar}
   	{}{}
   	{norbert.siegmund [at]}
   	{uni-weimar.de}
   	{+49 364 358 3850}	
}

\bigskip

\cvdoublecolumn{
	\cvreference{Sven Apel}
   	{Department of Informatics and Mathematics}
   	{University of Passau}
   	{}{}
   	{apel [at] uni-passau.de}
   	{}
   	{+49 851 509 3225}	
}
{
	\cvreference{Armando Solar-Lezama}
   	{Department of Electrical Engineering and Computer Science}
   	{Massachusetts Institute of Technology}
   	{}{}
   	{asolar [at] csail.mit.edu}
   	{}
   	{+1 617 258 9727}	
}

\end{document}
