\documentclass[11pt,letterpaper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{burgundy}
\setlength{\hintscolumnwidth}{2.5cm}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[scale=0.8]{geometry}
\usepackage[maxbibnames=99,
			defernumbers=true,
			isbn=false,
			doi=false,
			url=false,
			sorting=ymdnt,
			backend=biber,
			style=numeric,
			giveninits=true]{biblatex}
\usepackage[sfdefault]{roboto}

\renewcommand*{\intitlepunct}{\space}
\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{
  	\begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}
    \hfill
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}
    }
}
\newcommand{\cvreference}[8]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{~\texttt{#7}\newline}%
    \ifthenelse{\equal{#8}{}}{}{\phonesymbol~#8}}

\DeclareSortingScheme{ymdnt}{
  \sort{
    \field{presort}
  }
  \sort[final]{
    \field{sortkey}
  }
  \sort[direction=descending]{
    \field[strside=left,strwidth=4]{sortyear}
    \field[strside=left,strwidth=4]{year}
    \literal{9999}
  }
  \sort[direction=descending]{
    \field{month}
    \literal{9999}
  }
  \sort{
    \field{sortname}
    \field{author}
    \field{editor}
    \field{translator}
    \field{sorttitle}
    \field{title}
  }
  \sort{
    \field{sorttitle}
    \field{title}
  }
}

\AtDataInput{%
  \csnumgdef{entrycount:\therefsection:\thefield{entrytype}}{%
    \csuse{entrycount:\therefsection:\thefield{entrytype}}+1}}
    
\DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
\newrobustcmd*{\mkbibdesc}[1]{%
  \number\numexpr\csuse{entrycount:\therefsection:\thefield{entrytype}}+1-#1\relax}

\defbibenvironment{bibliography}
  {\list
     {\printtext[labelnumberwidth]{% label format from numeric.bbx
        \printfield{labelprefix}%
        \printfield{labelnumber}}}
     {\setlength{\topsep}{0pt}% layout parameters from moderncvstyleclassic.sty
      \setlength{\labelwidth}{\hintscolumnwidth}%
      \setlength{\labelsep}{\separatorcolumnwidth}%
      \leftmargin\labelwidth%
      \advance\leftmargin\labelsep}%
      \sloppy\clubpenalty4000\widowpenalty4000}
  {\endlist}
  {\item}  

\def\makenamesetup{%
  \def\bibnamedelima{~}%
  \def\bibnamedelimb{ }%
  \def\bibnamedelimc{ }%
  \def\bibnamedelimd{ }%
  \def\bibnamedelimi{ }%
  \def\bibinitperiod{.}%
  \def\bibinitdelim{~}%
  \def\bibinithyphendelim{.-}}    
\newcommand*{\makename}[2]{\begingroup\makenamesetup\xdef#1{#2}\endgroup}

\newcommand*{\boldname}[3]{%
  \def\lastname{#1}%
  \def\firstname{#2}%
  \def\firstinit{#3}}
\boldname{}{}{}

% Patch new definitions
\renewcommand{\mkbibnamegiven}[1]{%
  \ifboolexpr{ ( test {\ifdefequal{\firstname}{\namepartgiven}} or test {\ifdefequal{\firstinit}{\namepartgiven}} ) and test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\renewcommand{\mkbibnamefamily}[1]{%
  \ifboolexpr{ ( test {\ifdefequal{\firstname}{\namepartgiven}} or test {\ifdefequal{\firstinit}{\namepartgiven}} ) and test {\ifdefequal{\lastname}{\namepartfamily}} }
  {\mkbibbold{#1}}{#1}%
}

\boldname{Velez}{Miguel}{M.}

\name{Miguel}{Velez}
\title{Ph.D. Student in Software Engineering}
\address{Carnegie Mellon University}{School of Computer Science}{Institute for Software Research}
\email{mvelezce [at] cs.cmu.edu}
\homepage{http://www.cs.cmu.edu/\textasciitilde mvelezce/}
\social[linkedin]{miguelvelezmj25}

%\quote{"Premature optimization is the root of all evil" -Donald Knuth}
%\quote{"I never want to reach the point in my life where I've already done the most epic thing I will ever do" -Anonymous}


\begin{document}

\makecvtitle
\vspace*{-10mm}

\section{Education}
\cventry{2016 - Present}{Ph.D. Software Engineering}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{Advisor: Christian K{\"a}stner. Thesis Topic: White-Box Analysis of Configurable Systems.}
\cventry{2010 - 2015}{B.A. Computer Science (Physics minor) }{University of St Thomas}{St. Paul, MN}{USA}
	{Summa Cum Laude. Major and Minor GPA: 4.00/4.00. Cumulative GPA: 3.99/4.00.\\Advisor: Patrick Jarvis. Summa Cum Laude paper: ``Current and Future Relationships Between Robots and Humans''.}

\section{Industry Experience}
\subsection{Full-time}
\cventry{2016}{Application Developer/Software Engineer}{Sportradar US}{Minneapolis, MN}{USA}
	{Developed a Ruby ETL application that provided data for the NFL Radar360 research tool.}

\medskip

\subsection{Internships}
\cventry{Summer 2020}{Software Engineering Intern}{Google}{Remote, PA}{USA}
	{Collected and surfaced metrics corresponding to RPC behavior during integration tests.}
\cventry{Summer 2019}{Software Engineering Intern}{Google}{Sunnyvale, CA}{USA}
	{Designed and implemented a data federation GraphQL layer in CDAP/Cloud Data Fusion.}
\cventry{Summer 2018}{Software Engineering Intern}{Google}{Mountain View, CA}{USA}
	{Improved Suggest's ranking of contact actions in the Android Google Search App.}
\cventry{Fall 2015}{Application Developer/Software Engineer}{Sportradar US}{Minneapolis, MN}{USA}
	{Built a Ruby monitoring application to parse and build Formula 1 feeds.}
\cventry{Spring 2015}{Jr. Application Developer}{SportsData/Sportradar US}{Minneapolis, MN}{USA}
	{Implemented a Ruby application to parse and build MLB feeds.}
\cventry{2013 - 2014}{Cloud Developer Intern}{Valtira}{Minneapolis, MN}{USA}
	{Developed web applications with Java servlets, AngularJS, and MySQL databases.}

\section{Research Experience}
\cventry{2016 - Present}{Graduate Research Assistant}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{}{}
\cventry{Spring 2019}{Teaching Assistant - Analysis of Software Artifacts (Graduate course)}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{}{}
\cventry{Fall 2018}{Teaching Assistant - Foundations of Software Engineering (Undergraduate course)}{Carnegie Mellon University}{Pittsburgh, PA}{USA}{}{}
\cventry{Summer 2015}{Research Intern}{Massachusetts Institute of Technology}{Cambridge, MA}{USA}{}
	{}
\cventry{2014 - 2015}{Undergraduate Student Researcher}{University of St. Thomas}{St. Paul, MN}{USA}{}
	{}

\end{document}
